Flabby and injective objects in toposes

### 2022-02-14 paper-flabby-objects.tex
More precise assumptions for enough injectives

\begin{prop}\label{prop:basics-injective}
\begin{enumerate}
% Take care if numbering changes (referenced below)
\item Every set embeds canonically (that is, in a uniform fashion) into an injective set.
\item Every injective module is also injective as a set.
\item Assuming Zorn's lemma (but not the law of excluded middle, hence not the
axiom of choice), every module embeds into an
injective module.
\end{enumerate}\end{prop}

@@

>>>>

\begin{prop}\label{prop:basics-injective}
\begin{enumerate}
% Take care if numbering changes (referenced below)
\item Every set embeds canonically (that is, in a uniform fashion) into an injective set.
\item Every injective module is also injective as a set.
\item Assuming the axiom of choice (so Zorn's lemma in combination with the law of excluded middle), every module embeds into an
injective module.
\end{enumerate}\end{prop}

@@

We note in passing that Remark~\ref{rem:enough-injective-modules-without-lem}
below explains how to verify Proposition~\ref{prop:basics-injective}(3) also in
the absence of the law of excluded middle (but still requiring Zorn's lemma).
